Benchmarking FDR Methods - Alternative Settings

### 2017-10-20 datasets/simulations/analysis-01-plot.Rmd
Add p-value vs. covariate plots

```{r, load-libraries, message=FALSE}
library("dplyr")
library("ggplot2")
library("data.table")
library("SummarizedBenchmark")
```

```{r, load-helper-functions}
source("../R/plotsim_standardize.R")
source("../R/plotsim_average.R")
source("../R/plotsim_single.R")
```

@@

        ## adjusted p-values vs. standard error
        gp <- plotsim_single(sbas, sim_df, "SE", TRUE)
        ggsave(paste0(outp, "/SE-adjp-", gsub("(.*)\\.rdata", "\\1", basename(f)), ".png"),
               gp, width=10, height=9, units="in", dpi=200)
    }
}
```

>>>>

```{r, load-libraries, message=FALSE}
library("dplyr")
library("ggplot2")
library("viridis")
library("data.table")
library("SummarizedBenchmark")
```

```{r, load-helper-functions}
source("../R/plotsim_standardize.R")
source("../R/plotsim_average.R")
source("../R/plotsim_single.R")
source("../R/rank_scatter.R")
source("../R/strat_hist.R")
```

@@

        ## adjusted p-values vs. standard error
        gp <- plotsim_single(sbas, sim_df, "SE", TRUE)
        ggsave(paste0(outp, "/SE-adjp-", gsub("(.*)\\.rdata", "\\1", basename(f)), ".png"),
               gp, width=10, height=9, units="in", dpi=200)

        ## covariate rank vs. nlp (unadjusted)
        gp <- rank_scatter(sim_df, "pval", "ind_covariate") +
            scale_fill_viridis(option="viridis", direction=-1) +
            ggtitle("Informative Covariate Check")
        ggsave(paste0(outp, "/truep-heatmap-", gsub("(.*)\\.rdata", "\\1", basename(f)), ".png"),
               gp, width=10, height=6, units="in", dpi=200)

        ## stratified covariate vs. nlp (unadjusted)
        gp <- strat_hist(sim_df, "pval", "ind_covariate", maxy=5) +
            ggtitle("Informative Covariate Check")
        ggsave(paste0(outp, "/truep-barchart-", gsub("(.*)\\.rdata", "\\1", basename(f)), ".png"),
               gp, width=10, height=4, units="in", dpi=200)
    }
}
```
